IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-07 paper/appendix.tex
Minor updates about proofs, and some numbering fixes when referring to theorems.

\section{Formal Extensions}

>>>>

\section{Formal Extensions}
\label{sec:appendix-extensions}

Here we formally define the syntax and semantics of the extensions
sketched in Section~\ref{sec:extensions}.
In Figure~\ref{fig:labeled-vals} we show how labeled values can be added,
while Figure~\ref{fig:labeled-refs} details labeled references formally.
These changes to the semantics require us to update the erasure function
|erasef il|, which is shown in Figure~\ref{fig:erasure2}.
Note that the soundness proof in Appendix~\ref{sec:appendix}
is done for the fully extended language with labeled values and
labeled references.

### 2014-07-07 paper/proofs.tex
Minor updates about proofs, and some numbering fixes when referring to theorems.

In this section we prove all theorems we have stated.
We first observe that the non-interference claims for the languages
|specLang seqf targetLang| and |specLang roundrobinf targetLang|
in Theorems~\ref{thm:rr-tsni} and~\ref{thm:seq-tini} follow directly
from Theorems~\ref{thm:iso-tsni} and~\ref{thm:iso-tini},
respectively, where the set
of predicates is the set of always valid predicates (i.e., no restriction).

Before we proceed with the proof of Theorem~\ref{thm:iso-tsni},
we state a lemma we will use.

@@

\begin{proof}[Proof of Theorem~\ref{thm:iso-tsni}]
  We prove the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
  The base case for derivations
  of length 0 is trivial, allowing
  us to simply chose $|ic2'=ic2|$.  In the step case,
  we split the derivation sequence from~\eqref{eq:tsni-lhs} of length $n+1$ as follows:
  \[
  |ic1| |.->| |ic1''| |.->|^n |ic1'|
  \]
  for some configuration |ic1''|.  By Lemma~\ref{lemma:rr-tsni-general} to
  the first step and
  the induction hypothesis to the rest of the derivation sequence,
  we directly get the desired property.
  % long version
%  We proof the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
%  The base case for derivations
%  of length 0 is trivial, allowing
%  us to simple chose $|ic2'=ic2|$.  In the step case, we assume
%  the theorem holds for derivation sequences of length up to $n$, and show that it also
%  holds for those of length $n+1$.  We split the derivation sequence from~\eqref{eq:tsni-lhs} as follows:
%  \[
%  |ic1| |.->| |ic1''| |.->|^n |ic1'|
%  \]
%  for some configuration |ic1''|.  By Lemma~\ref{lemma:rr-tsni-general}, we get
%  |ic''| with
%  \begin{equation} \label{eq:tsni-proof-1}
%  |ic1''| \approx_{|il|} |ic2''|
%  \qquad \text{and} \qquad
%  |ic2| |.->|^* |ic2''|
%  \end{equation}
%  Applying the induction hypothesis to
%  $|ic1''| |.->|^n |ic1'|$, we get |ic2'| with
%  \begin{equation} \label{eq:tsni-proof-2}
%  |ic1'| \approx_{|il|} |ic2'|
%  \qquad \text{and} \qquad
%  |ic2''| |.->|^* |ic2'|
%  \end{equation}
%  Stitching together the derivation sequences from~\eqref{eq:tsni-proof-1} and~\eqref{eq:tsni-proof-2} directly gives
%  us the right-hand side of the implication in the TSNI
%  definition~\eqref{eq:tsni-rhs}, which concludes the proof.
\end{proof}
\begin{proof}[Proof sketch of Lemma~\ref{lemma:rr-tsni-general}]
  For space reasons, we only sketch the structure of the proof here.
  We refer the interested reader to the Appendix
  \ifextended
  \else
  of the extended version (which we provide at
  \url{http://www.scs.stanford.edu/~deian/ifc-inside_extended.pdf})
  \fi
  for a full proof.
  The proof distinguishes two cases:
  \begin{itemize}
    \item If the task |it1| executed in |ic1| is erased, then there is no
    need to take a step in |ic2|, as the computation in |ic1| does
    not have any visible effects after erasure.
    \item Otherwise, there must be a corresponding task |it2| in |ic2|, and
    it can take exactly the same reduction step as the task in |ic1|.
    The only difficulty is that there might be secret tasks executing
    before |it2|, but it can be shown that these do not influence the
    computation after erasure.
  \end{itemize}
\end{proof}
The proof of Theorem~\ref{thm:iso-tini} about TINI proceeds largely
in the same fashion as for Theorem~\ref{thm:iso-tsni} (TSNI), except that
some cases are simpler due to the fact termination is not an issue
(cf.~\cite{lio} for a TINI proof of a similar system).

>>>>

In this section we prove the theorems we have stated, or give a proof
sketch and refer to the extended version for the full proof.
We first observe that the non-interference claims for the languages
|specLang seqf targetLang| and |specLang roundrobinf targetLang|
in Theorems~\ref{thm:rr-tsni} and~\ref{thm:seq-tini} follow directly
from Theorem~\ref{thm:restricted}, where the set
of predicates is the set of always valid predicates (i.e., no restriction).

Before we proceed with the proof of Theorem~\ref{thm:restricted},
we state a lemma we will use.

@@

\begin{proof}[Proof of Theorem~\ref{thm:restricted}, TSNI]
  We prove the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
  The base case for derivations
  of length 0 is trivial, allowing
  us to simply chose $|ic2'=ic2|$.  In the step case,
  we split the derivation sequence from~\eqref{eq:tsni-lhs} of length $n+1$ as follows:
  \[
  |ic1| |.->| |ic1''| |.->|^n |ic1'|
  \]
  for some configuration |ic1''|.  By Lemma~\ref{lemma:rr-tsni-general} to
  the first step and
  the induction hypothesis to the rest of the derivation sequence,
  we directly get the desired property.
  % long version
%  We proof the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
%  The base case for derivations
%  of length 0 is trivial, allowing
%  us to simple chose $|ic2'=ic2|$.  In the step case, we assume
%  the theorem holds for derivation sequences of length up to $n$, and show that it also
%  holds for those of length $n+1$.  We split the derivation sequence from~\eqref{eq:tsni-lhs} as follows:
%  \[
%  |ic1| |.->| |ic1''| |.->|^n |ic1'|
%  \]
%  for some configuration |ic1''|.  By Lemma~\ref{lemma:rr-tsni-general}, we get
%  |ic''| with
%  \begin{equation} \label{eq:tsni-proof-1}
%  |ic1''| \approx_{|il|} |ic2''|
%  \qquad \text{and} \qquad
%  |ic2| |.->|^* |ic2''|
%  \end{equation}
%  Applying the induction hypothesis to
%  $|ic1''| |.->|^n |ic1'|$, we get |ic2'| with
%  \begin{equation} \label{eq:tsni-proof-2}
%  |ic1'| \approx_{|il|} |ic2'|
%  \qquad \text{and} \qquad
%  |ic2''| |.->|^* |ic2'|
%  \end{equation}
%  Stitching together the derivation sequences from~\eqref{eq:tsni-proof-1} and~\eqref{eq:tsni-proof-2} directly gives
%  us the right-hand side of the implication in the TSNI
%  definition~\eqref{eq:tsni-rhs}, which concludes the proof.
\end{proof}
\begin{proof}[Proof sketch of Lemma~\ref{lemma:rr-tsni-general}]
  For space reasons, we only sketch the structure of the proof here.
  We refer the interested reader to Appendix~\ref{sec:appendix}
  \ifextended
  \else
  of the extended version (which we provide at
  \url{http://www.scs.stanford.edu/~deian/ifc-inside_extended.pdf})
  \fi
  for a full proof.
  The proof distinguishes two cases:
  \begin{itemize}
    \item If the task |it1| executed in |ic1| is erased, then there is no
    need to take a step in |ic2|, as the computation in |ic1| does
    not have any visible effects after erasure.
    \item Otherwise, there must be a corresponding task |it2| in |ic2|, and
    it can take exactly the same reduction step as the task in |ic1|.
    The only difficulty is that there might be secret tasks executing
    before |it2|, but it can be shown that these do not influence the
    computation after erasure.
  \end{itemize}
\end{proof}
The proof of Theorem~\ref{thm:restricted} about TINI proceeds largely
in the same fashion as for TSNI, except that
some cases are simpler due to the fact termination is not an issue
(cf.~\cite{lio} for a TINI proof of a similar system).
